---
title: "CUPID-SEQ Fig 3 FINAL"
output: html_notebook
---

The following script includes analysis for examining the amplification bias between EMP and CUPID-seq protocols.

Beverly Fu

```{r Standard Setup}
# Configure directories, load libraries and base functions
source(paste0(here::here(), "/0-config.R"))

directory = paste0(here(), "/3-figures/")

output <- setup_tables(paste0(here(), "/1-data/DADA2_HS/"), '/1-data/HS-sample-info.xlsx')
ps <- output$ps # phyloseq object
taxa_order <- output$taxa_order # ASV plot order
samdf <- output$samdf # sample information
samdf$Sample <- rownames(samdf)

output2 <- setup_tables2(paste0(here(), "/1-data/DADA2_Long-read/"), '/1-data/HS-sample-info.xlsx')
ps2 <- output2$ps # phyloseq object
taxa_order2 <- output2$taxa_order # ASV plot order
samdf2 <- output2$samdf # sample information
samdf2$Sample <- rownames(samdf2)

cutoff_SI <- 0.001 # Supplementary Info ASV cutoff_SI
cutoff_MT <- 0.01 # Main Text ASV cutoff_SI (to minimize legend)
```

#######################################
# Fig. 3A: ASV relative abundance of EMP vs CUPID-Seq
#######################################

```{r Fig 3A}
ps2plot <- ps %>% subset_samples(!Phase %in% c("L2", "L3") # only one plate of DIP
                              & !Well %in% c("F01", "H01", "H12")) # remove blanks

taxa2keep <- psmelt(ps2plot %>% transform_sample_counts(function(x) x/sum(x))) %>% # convert to relative abundance
  filter(Abundance > cutoff_SI)

ps2plot <- prune_taxa(taxa2keep$OTU, ps2plot) %>%  # keep ASVs in taxa2keep
  transform_sample_counts(function(x) x/sum(x)) # renormalize

df2plot <- psmelt(ps2plot) # convert to long form
df2plot <- set_family_order(df2plot, taxa_order) # set Family2 order

transposed_df <- df2plot %>%
                 group_by(Subject, Well, Feature) %>%
                 mutate(EMP = ifelse(PCR == "EMP", ifelse(is.na(Abundance) | Abundance < cutoff_SI, 
                                      -3, log10(Abundance)), NA),
                 DIP = ifelse(PCR == "DIP", ifelse(is.na(Abundance) | Abundance < cutoff_SI, 
                                      -3, log10(Abundance)), NA)) %>%
                 select(Subject, Well, Feature, EMP, DIP) %>%
                 summarise(
                      EMP = pmax(max(EMP, na.rm = TRUE), -3),
                      DIP = pmax(max(DIP, na.rm = TRUE), -3),
                      .groups = "drop"
                 ) # Drop the grouping after summarization

transposed_df <- merge(transposed_df, taxa_order, by = "Feature")

correlation_result <- transposed_df %>%
  summarize(
    cor_value = cor(EMP, DIP, method = "pearson"),  # Pearson correlation coefficient
    p_value = cor.test(EMP, DIP, method = "pearson")$p.value,  # Extract p-value
    .groups = "drop")

correlation_result

g <- ggplot(transposed_df, aes(x = EMP, y = DIP, color = Color)) +
     geom_point(shape = 16, size = 1, stroke = 0.2, alpha = 0.5) +  # Fill color for the points
     scale_color_identity() +
     geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red", size = 0.3) +  # Add y = x line
     annotate(
        "text",
        x = -3, y = -0.25,
        label = bquote(italic(r) == .(round(correlation_result$cor_value, 2)) ~ "," ~ italic(p) == .(sprintf("%.2e", correlation_result$p_value))),
        color = "red", size = 2, hjust = 0
     ) +
     force_panelsizes(rows =  unit(c(4, 4, 4, 4), "cm"),
                      cols = unit(c(4, 4, 4, 4), "cm"), TRUE) +
     scale_y_continuous(breaks = c(0, -1, -2, -3, -4), limits = c(-3, 0)) + 
     scale_x_continuous(limits = c(-3, 0)) +
     labs(x = "log10(EMP ASV rel. abund.)", y = "log10(CUPID-seq ASV rel. abund.)") +
     theme_bw() +
     theme(legend.position = "none",
           panel.grid.major = element_blank(),      # Remove major grid lines
           panel.grid.minor = element_blank()) +     # Remove minor grid lines
     theme_custom_text() +
     coord_fixed()

ggsave(paste0(directory, "Fig3/Fig3A.pdf"), plot = g, device = "pdf", width = 2, height = 2)
```

#######################################
# Fig. S1A: ASV relative abundance of EMP vs CUPID-Seq, broken down by family
#######################################

```{r Fig S1}

g <- ggplot(transposed_df, aes(x = EMP, y = DIP, fill = Color)) +
     geom_point(shape = 21, size = 1, stroke = 0.2, alpha = 0.5, color = "black") +  # Fill color for the points
     scale_fill_identity() +
     geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red", size = 0.3) +  # Add y = x line
     facet_wrap(~Family2, labeller = labeller(Family2 = function(x) gsub("^f__", "", x))) +
     force_panelsizes(rows =  unit(c(2, 2, 2, 2), "cm"),
                      cols = unit(c(2, 2, 2, 2), "cm"), TRUE) +
     scale_y_continuous(breaks = c(0, -1, -2, -3, -4), limits = c(-3, 0)) + 
     scale_x_continuous(limits = c(-3, 0)) +
     labs(x = "log10(EMP ASV rel. abund.)", y = "log10(CUPID-seq ASV rel. abund.)") +
     theme_bw() +
     theme(legend.position = "none",
           panel.grid.major = element_blank(),      # Remove major grid lines
           panel.grid.minor = element_blank()) +     # Remove minor grid lines
     theme_custom_text() +
     coord_fixed()

ggsave(paste0(directory, "FigS1/FigS1A.pdf"), plot = g, device = "pdf", width = 6, height = 6)

```

#######################################
# Table S1A: Correlation of families
#######################################

```{r Table S1}

correlation_result1 <- transposed_df %>%
  filter(!(EMP == -3 & DIP == -3)) %>%
  group_by(Family2) %>%
  summarize(
    n = sum(complete.cases(EMP, DIP)),
    cor_value = if (n < 3 ||
                    sd(EMP, na.rm = TRUE) == 0 ||
                    sd(DIP, na.rm = TRUE) == 0) {
      NA_real_
    } else {
      cor(EMP, DIP, method = "pearson", use = "complete.obs")
    },
    p_value = if (n < 3 ||
                  sd(EMP, na.rm = TRUE) == 0 ||
                  sd(DIP, na.rm = TRUE) == 0) {
      NA_real_
    } else {
      cor.test(EMP, DIP, method = "pearson")$p.value
    },
    .groups = "drop"
  )

correlation_result1

write_xlsx(correlation_result1, paste0(here(), "/1-data/TableS1.xlsx"))
```

#######################################
# Fig. S3A: Calculating median fold change per family
#######################################

```{r Fig S3A}

ps2plot <- ps %>% subset_samples(!Phase %in% c("L2", "L3") # only one set of DIP
                              & !Well %in% c("F01", "H01", "H12")) # remove blanks

taxa2keep <- psmelt(ps2plot %>% transform_sample_counts(function(x) x/sum(x))) %>% # convert to relative abundance
  filter(Abundance > cutoff_SI) #

ps2plot <- prune_taxa(taxa2keep$OTU, ps2plot) %>%  # keep ASVs in taxa2keep
  transform_sample_counts(function(x) x/sum(x)) # renormalize

df2plot <- psmelt(ps2plot) # convert to long form
df2plot <- set_family_order(df2plot, taxa_order) # set Family2 order

fold_changes <- df2plot %>%
  select(Subject, Well) %>%
  distinct() %>%        # keeps only unique rows
  group_by(Subject, Well)

for (fam in unique(df2plot$Family2)) {
  transposed_df <- df2plot %>%
    filter(Family2 == fam) %>%
    group_by(Subject, Well, PCR) %>%
    summarise(Total_Abundance = sum(Abundance, na.rm = TRUE))
  
  transposed_df <- transposed_df %>%
                 group_by(Subject, Well) %>%
                 mutate(EMP = ifelse(PCR == "EMP", ifelse(is.na(Total_Abundance) | Total_Abundance < cutoff_SI, 
                                      cutoff_SI, Total_Abundance), NA),
                 DIP = ifelse(PCR == "DIP", ifelse(is.na(Total_Abundance) | Total_Abundance < cutoff_SI, 
                                      cutoff_SI, Total_Abundance), NA)) %>%
                 select(Subject, Well, EMP, DIP) %>%
                 summarise(
                    EMP = max(EMP, na.rm = TRUE),
                    DIP = max(DIP, na.rm = TRUE),
                    .groups = 'drop') # Drop the grouping after summarization

  transposed_df <- transposed_df %>% mutate(!!fam := DIP / EMP)
  transposed_df <- transposed_df %>%
    mutate(!!fam := if_else(EMP != cutoff_SI & DIP != cutoff_SI, !!sym(fam), NA_real_))
  
  fold_changes = merge(fold_changes, transposed_df[, c("Subject", "Well", fam)],, by = c("Subject", "Well"))
}

fold_changes_long <- fold_changes %>%
  pivot_longer(
    cols = -c(Subject, Well),  # all columns except Subject and Well
    names_to = "Family",       # column to hold the original column names
    values_to = "Value"        # column to hold the values
  )

fold_changes_long <- merge(fold_changes_long, unique(taxa_order %>% select("Family2", "Color")), by.x = "Family", by.y = "Family2")

# Compute median per Family
medians <- fold_changes_long %>%
  group_by(Family, Color) %>%
  summarise(median_value = median(Value, na.rm = TRUE))

g <- ggplot(fold_changes_long, aes(x = Value, fill = Color)) + 
      geom_histogram(bins = 25, color = "black", linewidth = 0.2) +
      scale_y_continuous(breaks = c(0, 40, 80, 120, 160)) +
      facet_wrap(~Family, labeller = labeller(Family = function(x) gsub("^f__", "", x))) +
      scale_fill_identity() +
      geom_vline(data = medians, aes(xintercept = median_value), linetype = "dashed", color = "red", size = 0.3) +
      geom_text(
          data = medians,
          aes(x = median_value + 1, y = 100, label = paste0("med = ", round(median_value, 2))),
          color = "red", size = 2, hjust = 0
          ) +
      labs(x = "Fold change of ASVs by family", y = "Counts") +
      theme_bw() +
         theme(legend.position = "none",
               panel.grid.major = element_blank(),      # Remove major grid lines
               panel.grid.minor = element_blank()) +     # Remove minor grid lines
      theme_custom_text()

ggsave(paste0(directory, "FigS2/FigS2A.pdf"), plot = g, device = "pdf", width = 6, height = 4)
```

#######################################
# Fig. S3B: Normalization
#######################################

```{r Fig 3B}

# Need to run S3A section

ps2plot <- ps %>% subset_samples(!Phase %in% c("L2", "L3") # only one set of DIP
                              & !Well %in% c("F01", "H01", "H12")) # remove blanks

taxa2keep <- psmelt(ps2plot %>% transform_sample_counts(function(x) x/sum(x))) %>% # convert to relative abundance
  filter(Abundance > cutoff_SI) #

ps2plot <- prune_taxa(taxa2keep$OTU, ps2plot) %>%  # keep ASVs in taxa2keep
  transform_sample_counts(function(x) x/sum(x)) # renormalize

ps_long <- psmelt(ps2plot)

# Rescale abundances conditionally
ps_long <- ps_long %>%
  left_join(medians, by = c("Family2" = "Family")) %>%  # add median_value per Family2
  mutate(Abundance = if_else(
    PCR == "DIP" & !is.na(median_value),
    Abundance / median_value,   # divide by family median
    Abundance                   # otherwise keep original
  )) 

# Convert back to phyloseq object
# Keep OTU table, sample data, taxonomy
otu_new <- ps_long %>%
  select(Sample, OTU, Abundance) %>%
  pivot_wider(
    names_from = Sample, 
    values_from = Abundance, 
    values_fill = 0
  ) %>%
  column_to_rownames("OTU") %>%
  as.matrix()  # MUST be a matrix for phyloseq

# Replace OTU table in phyloseq object
otu_table(ps2plot) <- otu_table(otu_new, taxa_are_rows = TRUE)


ps2plot <- prune_taxa(taxa2keep$OTU, ps2plot) %>%  # keep ASVs in taxa2keep
  transform_sample_counts(function(x) x/sum(x)) # renormalize

df2plot <- psmelt(ps2plot) # convert to long form
df2plot <- set_family_order(df2plot, taxa_order) # set Family2 order

transposed_df <- df2plot %>%
                 group_by(Subject, Well, Feature) %>%
                 mutate(EMP = ifelse(PCR == "EMP", ifelse(is.na(Abundance) | Abundance < cutoff_SI, 
                                      -3, log10(Abundance)), NA),
                 DIP = ifelse(PCR == "DIP", ifelse(is.na(Abundance) | Abundance < cutoff_SI, 
                                      -3, log10(Abundance)), NA)) %>%
                 select(Subject, Well, Feature, EMP, DIP) %>%
                 summarise(
                    EMP = max(EMP, na.rm = TRUE),
                    DIP = max(DIP, na.rm = TRUE),
                    .groups = 'drop') # Drop the grouping after summarization

transposed_df <- merge(transposed_df, taxa_order, by = "Feature")

family2_scale <- get_color_mapping(transposed_df) # legend colors

correlation_result <- transposed_df %>%
  summarize(
    cor_value = cor(EMP, DIP, method = "pearson"),  # Pearson correlation coefficient
    p_value = cor.test(EMP, DIP, method = "pearson")$p.value,  # Extract p-value
    .groups = "drop")

correlation_result

g <- ggplot(transposed_df, aes(x = EMP, y = DIP, color = Color)) +
     geom_point(shape = 16, size = 1, stroke = 0.2, alpha = 0.5) +  # Fill color for the points
     scale_color_identity() +
     geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red", size = 0.3) +  # Add y = x line
     annotate(
        "text",
        x = -3, y = -0.25,
        label = bquote(italic(r) == .(round(correlation_result$cor_value, 2)) ~ "," ~ italic(p) == .(sprintf("%.2e", correlation_result$p_value))),
        color = "red", size = 2, hjust = 0
     ) +
     force_panelsizes(rows =  unit(c(4, 4, 4, 4), "cm"),
                      cols = unit(c(4, 4, 4, 4), "cm"), TRUE) +
     scale_y_continuous(breaks = c(0, -1, -2, -3, -4), limits = c(-3, 0)) + 
     scale_x_continuous(limits = c(-3, 0)) +
     labs(x = "log10(EMP ASV rel. abund.)", y = "log10(CUPID-seq ASV rel. abund.)") +
     theme_bw() +
     theme(legend.position = "none",
           panel.grid.major = element_blank(),      # Remove major grid lines
           panel.grid.minor = element_blank()) +     # Remove minor grid lines
     theme_custom_text() +
     coord_fixed()

ggsave(paste0(directory, "Fig3/Fig3B.pdf"), plot = g, device = "pdf", width = 2, height = 2)

correlation_result1 <- transposed_df %>%
  filter(!(EMP == -3 & DIP == -3)) %>%
  group_by(Family2) %>%
  summarize(
    n = sum(complete.cases(EMP, DIP)),
    cor_value = if (n < 3 ||
                    sd(EMP, na.rm = TRUE) == 0 ||
                    sd(DIP, na.rm = TRUE) == 0) {
      NA_real_
    } else {
      cor(EMP, DIP, method = "pearson", use = "complete.obs")
    },
    p_value = if (n < 3 ||
                  sd(EMP, na.rm = TRUE) == 0 ||
                  sd(DIP, na.rm = TRUE) == 0) {
      NA_real_
    } else {
      cor.test(EMP, DIP, method = "pearson")$p.value
    },
    .groups = "drop"
  )

correlation_result1

ggsave(paste0(directory, "Fig3/Fig3B.pdf"), plot = g, device = "pdf", width = 2, height = 2)
```

```{r Fig S2B}

g <- ggplot(transposed_df, aes(x = EMP, y = DIP, fill = Color)) +
     geom_point(shape = 21, size = 1, stroke = 0.2, alpha = 0.5, color = "black") +  # Fill color for the points
     scale_fill_identity() +
     geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red", size = 0.3) +  # Add y = x line
     facet_wrap(~Family2, labeller = labeller(Family2 = function(x) gsub("^f__", "", x))) +
     force_panelsizes(rows =  unit(c(2, 2, 2, 2), "cm"),
                      cols = unit(c(2, 2, 2, 2), "cm"), TRUE) +
     scale_y_continuous(breaks = c(0, -1, -2, -3, -4), limits = c(-3, 0)) + 
     scale_x_continuous(limits = c(-3, 0)) +
     labs(x = "log10(EMP ASV rel. abund.)", y = "log10(CUPID-seq ASV rel. abund.)") +
     theme_bw() +
     theme(legend.position = "none",
           panel.grid.major = element_blank(),      # Remove major grid lines
           panel.grid.minor = element_blank()) +     # Remove minor grid lines
     theme_custom_text() +
     coord_fixed()

ggsave(paste0(directory, "FigS2/FigS2B.pdf"), plot = g, device = "pdf", width = 6, height = 6)

```

```{r Table S2}

correlation_result2 <- transposed_df %>%
  filter(!(EMP == -3 & DIP == -3)) %>%
  group_by(Family2) %>%
  summarize(
    n = sum(complete.cases(EMP, DIP)),
    cor_value = if (n < 3 ||
                    sd(EMP, na.rm = TRUE) == 0 ||
                    sd(DIP, na.rm = TRUE) == 0) {
      NA_real_
    } else {
      cor(EMP, DIP, method = "pearson", use = "complete.obs")
    },
    p_value = if (n < 3 ||
                  sd(EMP, na.rm = TRUE) == 0 ||
                  sd(DIP, na.rm = TRUE) == 0) {
      NA_real_
    } else {
      cor.test(EMP, DIP, method = "pearson")$p.value
    },
    .groups = "drop"
  )

correlation_result2

write_xlsx(correlation_result2, paste0(here(), "/1-data/TableS2.xlsx"))
```

#######################################
# Fig. 3C: Bray-Curtis distance
#######################################

```{r Fig 3C}

ps2plot <- ps %>% subset_samples(!Well %in% c("F01", "H01", "H12")
                                 & Phase %in% c("L0", "L1", "NA")) # remove blanks

taxa2keep <- psmelt(ps2plot %>% transform_sample_counts(function(x) x/sum(x))) %>% # convert to relative abundance
  filter(Abundance > cutoff_SI) #

ps2plot <- prune_taxa(taxa2keep$OTU, ps2plot) %>%  # keep ASVs in taxa2keep
  transform_sample_counts(function(x) x/sum(x)) # renomalize

df2plot <- psmelt(ps2plot) # convert to long form
df2plot <- set_family_order(df2plot, taxa_order) # set Family2 order

set.seed(100) # Consistent pcoa
ps2ordinate <- ps2plot # Choose which samples you want to ordinate
otu_table_ps <- otu_table(ps2ordinate)

otu_table_ps_clean <- otu_table_ps[rowSums(otu_table_ps) > 0, ] # Remove rows with all zeros (empty OTU rows)
otu_table_ps_clean <- otu_table_ps_clean[rowSums(otu_table_ps_clean > 0) >= 3, ] # Remove OTUs present in < 3 samples

retained_otus <- taxa_names(otu_table_ps_clean)

# Subset all components accordingly
ps_clean <- merge_phyloseq(
  otu_table(otu_table_ps_clean),
  sample_data(ps),
  tax_table(ps)[retained_otus, ],
  phy_tree(ps)
)

ps_clean <- prune_taxa(retained_otus, ps_clean)

bc_dist <- phyloseq::distance(ps_clean, method = "bray")
bc_mat  <- as.matrix(bc_dist)

bc_long <- bc_mat %>%
  as_tibble(rownames = "sample1") %>%
  pivot_longer(-sample1, names_to = "sample2", values_to = "distance") %>%
  filter(sample1 < sample2)  # upper triangle only

samdf <- as(sample_data(ps_clean), "data.frame") %>%
  rownames_to_column("Sample")

meta1 <- samdf %>%
  rename(sample1 = Sample) %>%
  rename_with(~ paste0(., "1"), -sample1)

meta2 <- samdf %>%
  rename(sample2 = Sample) %>%
  rename_with(~ paste0(., "2"), -sample2)

bc_long_meta <- bc_long %>%
  left_join(meta1, by = "sample1") %>%
  left_join(meta2, by = "sample2")

bc_filtered <- bc_long_meta %>%
  filter( (Platform1 == "MiSeq"  & Platform2 == "NovaSeq") |
          (Platform1 == "NovaSeq" & Platform2 == "MiSeq")) %>%
  mutate(
    label = if_else(
      Subject1 == Subject2 & Well1 == Well2 & Drug1 == Drug2,
      "Same", "Different"
    )
  )

g <- ggplot(bc_filtered, aes(x = distance, fill = label)) +
  geom_histogram(binwidth = 0.05, color = "black", linewidth = 0.2) +
  facet_grid(rows = vars(label), scales = "free_y") +
  scale_fill_manual(values = c("Same" = "#FF0000", "Diff" = "grey")) +
  labs(
    x = "Bray-Curtis distance",
    y = "Count",
    fill = "Comparison"
  ) +
   theme_bw() +
   theme(legend.position = "none",
         panel.grid.major = element_blank(),      # Remove major grid lines
         panel.grid.minor = element_blank()) +     # Remove minor grid lines
   theme_custom_text()

ggsave(paste0(directory, "Fig3/Fig3C.pdf"), plot = g, device = "pdf", width = 2, height = 2)
```

#######################################
# Fig. 3D: Long-read sequencing
#######################################

```{r Fig 3D}

ps2plot <- ps2

taxa2keep <- psmelt(ps2plot %>% transform_sample_counts(function(x) x/sum(x))) %>% # convert to relative abundance
  filter(Abundance > cutoff_MT) # identify taxa with relative abundances greater than cutoff

ps2plot <- prune_taxa(taxa2keep$OTU, ps2plot) %>% # keep ASVs in taxa2keep
  transform_sample_counts(function(x) x/sum(x)) # renormalize

df2plot <- psmelt(ps2plot) %>% # convert to long form
  mutate(PCR = factor(PCR, levels = c("EMP", "CUPID-seq", "Full"), ordered = TRUE))
df2plot <- set_family_order(df2plot, taxa_order2) # set Family2 order

family2_scale <- get_color_mapping(df2plot) # legend colors

g <- ggplot(df2plot, aes(x = 1, y = Abundance, fill = Family2)) + 
     geom_bar(aes(x = PCR), position = "stack", stat = "identity", color = "black", linewidth = 0.1) + 
     scale_y_continuous("Relative Abundance", breaks = c(0.00, 0.25, 0.50, 0.75, 1.00)) +
     scale_fill_manual(values = family2_scale$values, breaks = family2_scale$breaks, labels = family2_scale$labels) +
     facet_nested(cols = vars(Sample_num), scales = "free", space = "free") +
     theme_bw() +
     theme(axis.ticks.y = element_blank(),
           axis.title.x = element_blank(),
           axis.text.x = element_text(size = 6, angle = 90, hjust = 1), 
           axis.ticks.x = element_blank(),
           panel.background = element_blank(),
           panel.grid.major = element_blank(),      # Remove major grid lines
           panel.grid.minor = element_blank(),
           legend.position = "none") + # no legend 
     theme_custom_text()

ggsave(paste0(directory, "Fig3/Fig3D.pdf"), plot = g, device = "pdf", width = 2, height = 2)

g <- ggplot(df2plot, aes(x = 1, y = Abundance, fill = Family2)) + 
     geom_bar(aes(x = PCR), position = "stack", stat = "identity", color = "black", linewidth = 0.1) + 
     scale_y_continuous("Relative Abundance", breaks = c(0.00, 0.25, 0.50, 0.75, 1.00)) +
     scale_fill_manual(values = family2_scale$values, breaks = family2_scale$breaks, labels = family2_scale$labels) +
     facet_nested(cols = vars(Sample_num), scales = "free", space = "free") +
     theme_custom_text() +
     theme(legend.text = element_text(size = 5),  # Legend text size
           legend.key.size = unit(0.2, "cm")) +
     guides(fill = guide_legend(ncol = 1, byrow = FALSE)) + # Legend columns, fill legend items by column
     labs(fill = "Family") # Change legend label

# Extract and display only the legend
legend <- get_legend(g)

ggsave(paste0(directory, "Fig3/Fig3D_legend.pdf"), plot = legend, device = "pdf", width = 2.5, height = 2.5)

```